Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea

### 2020-05-15 analysis/paper/paper.Rmd
updated

>>>>

cv_by_site_df_label_more_than_10_ml_mw_bl <- 
cv_by_site_df_label_more_than_10 %>%
  pivot_longer(cols = -c(site_phase, label), 
               names_to = "lithic_attribute",
               values_to = "CV") %>%
  filter(lithic_attribute %in% c("ML", "BL","MW"))  %>% 
  mutate(phase = parse_number(str_extract(site_phase, "_."))) %>% 
  group_by(site_phase) %>% 
  mutate(mean_cv = mean(CV))

  ggplot(cv_by_site_df_label_more_than_10_ml_mw_bl,
         aes(x = lithic_attribute, 
             y = CV)) +
  geom_col() +
  geom_hline(aes(yintercept = mean_cv), 
             colour = "red") +
  facet_wrap(~  label) +
  ggtitle("CVs of point attributes by site (with sites >=7 artefacts)") +
  theme_minimal()
```
